---
title: Forecast reconciliation
subtitle: 4. Temporal & cross-temporal forecast reconciliation
author: Rob J Hyndman
pdf-engine: pdflatex
fig-width: 9
fig-height: 4.5
format:
  beamer:
    theme: monash
    aspectratio: 169
    fontsize: 14pt
    section-titles: false
    knitr:
      opts_chunk:
        dev: "CairoPDF"
include-in-header: header.tex
cite-method: biblatex
bibliography: hts.bib
biblio-title: References
keep-tex: true
highlight-style: tango
execute:
  echo: false
  message: false
  warning: false
  cache: true
---

```{r}
source("setup.R")
```

## Notation reminder

\begin{textblock}{8.5}(0.3,1.4)
Every collection of time series with linear constraints can be written as
\centerline{\colorbox[RGB]{210,210,210}{$\bY_{t}=\color{blue}\bS\color{red}\bm{b}_{t}$}}
\vspace*{-0.9cm}\begin{itemize}\parskip=0cm\itemsep=0cm
  \item $\by_t=$ vector of all series at time $t$
  \item $ y_{\text{Total},t}= $ aggregate of all series at time
        $t$.
  \item $ y_{X,t}= $ value of series $X$ at time $t$.
  \item $\color{red}{\bm{b}_t}=$ vector of most disaggregated series at time $t$
  \item $\color{blue}{\bS}=$ ``summing matrix'' containing the linear constraints.
\end{itemize}
\end{textblock}

\begin{textblock}{5.7}(11.2,0.3)
\begin{minipage}{4cm}
  \begin{block}{}\centering
    \begin{tikzpicture}
      \tikzstyle{every node}=[ellipse,draw,fill=red!15,inner sep=2pt]
      \tikzstyle[level distance=.3cm]
      \tikzstyle[sibling distance=12cm]
      \tikzstyle{level 1}=[sibling distance=10mm,font=\small,set style={{every node}+=[fill=blue!15]}]
      \node{Total}[edge from parent fork down]
      child {node {A}
        }
      child {node {B}
        }
      child {node {C}
        };
    \end{tikzpicture}
  \end{block}
\end{minipage}
\end{textblock}

\only<1>{\begin{textblock}{5.7}(9.2,2.8)\fontsize{14}{15}\sf
  \begin{align*}
    \bY_{t} & = \begin{pmatrix}
                  y_{\text{Total},t} \\
                  y_{A,t}            \\
                  y_{B,t}            \\
                  y_{C,t}
                \end{pmatrix}                             \\
            & = {\color{blue}\underbrace{\begin{pmatrix}
                                              1 & 1 & 1 \\
                                              1 & 0 & 0 \\
                                              0 & 1 & 0 \\
                                              0 & 0 & 1
                                            \end{pmatrix}}_{\bS}}
    {\color{red}\underbrace{\begin{pmatrix}
                                y_{A,t} \\y_{B,t}\\y_{C,t}
                              \end{pmatrix}}_{\bm{b}_{t}}}
  \end{align*}
\end{textblock}}
\only<2>{\begin{textblock}{5.7}(9.2,3.3)\fontsize{14}{15}\sf
  \begin{alertblock}{}
    \begin{itemize}\itemsep=0.1cm
      \item Base forecasts: $\hat{\bm{y}}_{T+h|T}$
      \item Reconciled forecasts: $\tilde{\bm{y}}_{T+h|T}=\bS\bm{G}\hat{\bm{y}}_{T+h|T}$
      \item MinT: $\bG = (\bS'\bm{W}_h^{-1}\bS)^{-1}\bS'\bm{W}_h^{-1}$ where $\bm{W}_h$ is covariance matrix of base forecast errors.
    \end{itemize}
  \end{alertblock}
\end{textblock}}

# Temporal reconciliation

## Temporal reconciliation: quarterly data

\begin{textblock}{7}(1,1.9)
\begin{tikzpicture}
  \tikzstyle{every node}=[ellipse,draw,inner sep=0.2pt,fill=red!15,font=\small]
  \tikzstyle[level distance=.1cm]
  \tikzstyle[sibling distance=3cm]
  \tikzstyle{level 1}=[sibling distance=18mm,set style={{every node}+=[fill=yellow]}]
  \node{Annual}[edge from parent fork down]
  child {node {Q$_1$}}
  child {node {Q$_2$}}
  child {node {Q$_3$}}
  child {node {Q$_4$}};
\end{tikzpicture}
\end{textblock}

\only<3>{\begin{textblock}{8.5}(8.3,1.1)\fontsize{14}{17}\sf
$$\bm{y}_\tau =
  \begin{bmatrix}
    x_{\tau}^{[4]}  \\[0.2cm]
    x_{\tau,1}^{[1]} \\[0.2cm]
    x_{\tau,2}^{[1]} \\[0.2cm]
    x_{\tau,3}^{[1]} \\[0.2cm]
    x_{\tau,4}^{[1]}
  \end{bmatrix}
  \qquad
  \bm{S} = \begin{bmatrix}
    1 & 1 & 1 & 1 \\[0.2cm]
    1 & 0 & 0 & 0 \\[0.2cm]
    0 & 1 & 0 & 0 \\[0.2cm]
    0 & 0 & 1 & 0 \\[0.2cm]
    0 & 0 & 0 & 1
  \end{bmatrix}
$$
\end{textblock}}

\only<2->{\begin{textblock}{8}(.3,5.7)
  \begin{alertblock}{}
    \begin{itemize}
      \item[\color{white}\ding{229}] Forecast series at each available frequency.
      \item[\color{white}\ding{229}] Optimally combine forecasts within the same year.
    \end{itemize}
  \end{alertblock}
\end{textblock}}

\only<3->{\begin{textblock}{5}(10.3,7.9)
\fontsize{11}{12}\sf
$\tau=$ index of largest temporal aggregation level.
\end{textblock}}


## Temporal reconciliation: quarterly data

\begin{textblock}{7}(0.1,1.9)
\begin{tikzpicture}
  \tikzstyle{every node}=[ellipse,draw,inner sep=0.2pt,fill=red!15,font=\small]
  \tikzstyle[level distance=.1cm]
  \tikzstyle[sibling distance=3cm]
  \tikzstyle{level 1}=[sibling distance=42mm,set style={{every node}+=[fill=blue!15]}]
  \tikzstyle{level 2}=[sibling distance=18mm,set style={{every node}+=[fill=yellow]}]
  \node{Annual}[edge from parent fork down]
  child {node {Semi-Annual$_1$}
      child {node {Q$_1$}}
      child {node {Q$_2$}}
    }
  child {node {Semi-Annual$_2$}
      child {node {Q$_3$}}
      child {node {Q$_4$}}
    };
\end{tikzpicture}
\end{textblock}

\begin{textblock}{8.5}(8.3,1.1)\fontsize{14}{17}\sf
$$\bm{y}_\tau =
  \begin{bmatrix}
    x_{\tau}^{[4]}  \\[0.2cm]
    x_{\tau,1}^{[2]} \\[0.2cm]
    x_{\tau,2}^{[2]} \\[0.2cm]
    x_{\tau,1}^{[1]} \\[0.2cm]
    x_{\tau,2}^{[1]} \\[0.2cm]
    x_{\tau,3}^{[1]} \\[0.2cm]
    x_{\tau,4}^{[1]}
  \end{bmatrix}
  \qquad
  \bm{S} = \begin{bmatrix}
    1 & 1 & 1 & 1 \\[0.2cm]
    1 & 1 & 0 & 0 \\[0.2cm]
    0 & 0 & 1 & 1 \\[0.2cm]
    1 & 0 & 0 & 0 \\[0.2cm]
    0 & 1 & 0 & 0 \\[0.2cm]
    0 & 0 & 1 & 0 \\[0.2cm]
    0 & 0 & 0 & 1
  \end{bmatrix}
$$
\end{textblock}

\begin{textblock}{8}(.3,5.7)
  \begin{alertblock}{}
    \begin{itemize}
      \item[\color{white}\ding{229}] Forecast series at each available frequency.
      \item[\color{white}\ding{229}] Optimally combine forecasts within the same year.
    \end{itemize}
  \end{alertblock}
\end{textblock}

\begin{textblock}{5}(10.3,7.9)
\fontsize{11}{12}\sf
$\tau=$ index of largest temporal aggregation level.
\end{textblock}

## Temporal reconciliation: monthly data

\only<1>{\begin{tikzpicture}
  \tikzstyle{every node}=[ellipse,draw,inner sep=0.2pt,fill=red!15,font=\small]
  \tikzstyle[level distance=.1cm]
  \tikzstyle[sibling distance=7cm]
  \tikzstyle{level 1}=[sibling distance=72mm,set style={{every node}+=[fill=blue!15]}]
  \tikzstyle{level 2}=[sibling distance=36mm,set style={{every node}+=[fill=yellow]}]
  \tikzstyle{level 3}=[sibling distance=12mm,font=\scriptsize,set style={{every node}+=[fill=green]}]
  \node{Annual}[edge from parent fork down]
  child {node {Semi-Annual$_1$}
      child {node {Q$_1$}
          child {node {\scriptsize M$_1$}}
          child {node {\scriptsize M$_2$}}
          child {node {\scriptsize M$_3$}}
        }
      child {node {Q$_2$}
          child {node {\scriptsize M$_4$}}
          child {node {\scriptsize M$_5$}}
          child {node {\scriptsize M$_6$}}
        }
    }
  child {node {Semi-Annual$_2$}
      child {node {Q$_3$}
          child {node {\scriptsize M$_7$}}
          child {node {\scriptsize M$_8$}}
          child {node {\scriptsize M$_9$}}
        }
      child {node {Q$_4$}
          child {node {\scriptsize M$_{10}$}}
          child {node {\scriptsize M$_{11}$}}
          child {node {\scriptsize M$_{12}$}}
        }
    };
\end{tikzpicture}}
\only<2->{\begin{tikzpicture}
  \tikzstyle{every node}=[ellipse,draw,inner sep=0.2pt,fill=red!15,font=\small]
  \tikzstyle[level distance=.1cm]
  \tikzstyle[sibling distance=7cm]
  \tikzstyle{level 1}=[sibling distance=48mm,set style={{every node}+=[fill=blue!15]}]
  \tikzstyle{level 2}=[sibling distance=24mm,set style={{every node}+=[fill=yellow]}]
  \tikzstyle{level 3}=[sibling distance=12mm,set style={{every node}+=[fill=green]}]
  \node{Annual}[edge from parent fork down]
  child {node {FourM$_1$}
      child {node {BiM$_1$}
          child {node {\scriptsize M$_1$}}
          child {node {\scriptsize M$_2$}}
        }
      child {node {BiM$_2$}
          child {node {\scriptsize M$_3$}}
          child {node {\scriptsize M$_4$}}
        }
    }
  child {node {FourM$_2$}
      child {node {BiM$_3$}
          child {node {\scriptsize M$_5$}}
          child {node {\scriptsize M$_6$}}
        }
      child {node {BiM$_4$}
          child {node {\scriptsize M$_7$}}
          child {node {\scriptsize M$_8$}}
        }
    }
  child {node {FourM$_3$}
      child {node {BiM$_5$}
          child {node {\scriptsize M$_9$}}
          child {node {\scriptsize M$_{10}$}}
        }
      child {node {BiM$_6$}
          child {node {\scriptsize M$_{11}$}}
          child {node {\scriptsize M$_{12}$}}
        }
    };
\end{tikzpicture}}\pause

\begin{textblock}{14}(1,6.7)
  \begin{alertblock}{}
    \begin{itemize}
      \item[\color{white}\ding{229}] Forecast series at each available frequency.
      \item[\color{white}\ding{229}] Optimally combine forecasts within the same year.
    \end{itemize}
  \end{alertblock}
\end{textblock}

## Temporal reconciliation: monthly data
\fontsize{11}{11}\sf

$$
  \bm{y}_\tau=\begin{bmatrix}
    x_{\tau}^{[12]}     \\[0.2cm]
    \bm{x}_{\tau}^{[6]} \\[0.2cm]
    \bm{x}_{\tau}^{[4]} \\[0.2cm]
    \bm{x}_{\tau}^{[3]} \\[0.2cm]
    \bm{x}_\tau^{[2]}   \\[0.2cm]
    \bm{x}_\tau^{[1]}
  \end{bmatrix}
  \qquad
  \bm{S} = \begin{bmatrix}
    1                & 1 & 1 & 1 & 1~~~1~~~1~~~1 & 1 & 1 & 1 & 1 \\
    1                & 1 & 1 & 1 & 1~~~1~~~0~~~0 & 0 & 0 & 0 & 0 \\
    0                & 0 & 0 & 0 & 0~~~0~~~1~~~1 & 1 & 1 & 1 & 1 \\
    1                & 1 & 1 & 1 & 0~~~0~~~0~~~0 & 0 & 0 & 0 & 0 \\
    0                & 0 & 0 & 0 & 1~~~1~~~1~~~1 & 0 & 0 & 0 & 0 \\
    0                & 0 & 0 & 0 & 0~~~0~~~0~~~0 & 1 & 1 & 1 & 1 \\
    1                & 1 & 1 & 0 & 0~~~0~~~0~~~0 & 0 & 0 & 0 & 0 \\
                     &   &   &   & \vdots        &   &   &   &   \\
    0                & 0 & 0 & 0 & 0~~~0~~~0~~~0 & 0 & 1 & 1 & 1 \\
    1                & 1 & 0 & 0 & 0~~~0~~~0~~~0 & 0 & 0 & 0 & 0 \\
                     &   &   &   & \vdots        &   &   &   &   \\
    0                & 0 & 0 & 0 & 0~~~0~~~0~~~0 & 0 & 0 & 1 & 1 \\[0.2cm]
    \phantom{\vdots} &   &   &   & \bm{I}_{12}   &   &   &   &
  \end{bmatrix}
$$

## Temporal reconciliation
\fontsize{14}{15}\sf

For a time series  $y_1,\dots,y_T$, observed at frequency $m$:
\begin{alertblock}{}\vspace*{-0.1cm}
$$
  x_j^{[k]} = \sum_{t = (j-1)k+1}^{jk} y_t\qquad \text{for $j = 1,\dots,\lfloor T/k\rfloor$}
$$
\end{alertblock}
* $k \in \mathcal{K} = \{k_1,\dots,k_p\}$ denote the $p$ factors of $m$ in ascending order, where $k_1=1$ and $k_p=m$
* $x_j^{[1]} = y_t$
* A single unique hierarchy is only possible when there are no coprime pairs in $\mathcal{K}$.
* $M_k=m/k$ is seasonal period of aggregated series.

## Temporal reconciliation
\fontsize{14}{15}\sf\vspace*{-0.5cm}
$$\bm{x}_\tau = \bm{S} \bm{x}_\tau^{[1]}, \qquad \bm{S} = \begin{bmatrix}\bm{A}\\\bm{I}\end{bmatrix}$$
where
$$
\bm{x}_\tau = \begin{bmatrix*}[l]
    {x_\tau^{[k_p]}}\\
    {\bm{x}_\tau^{[k_{p-1}]}}\\
    \quad\vdots\\
    {\bm{x}_\tau^{[k_1]}}\\
  \end{bmatrix*}\qquad
  \bm{x}_\tau^{[k]} = \begin{bmatrix*}[l]
    x_{M_k(\tau-1)+1}^{[k]}\\
    x_{M_k(\tau-1)+2}^{[k]}\\
    \quad\vdots\\
    x_{M_k\tau}^{[k]}
  \end{bmatrix*}\qquad
\bm{A} =
  \begin{bmatrix}
    \bm{1}'_m                                    \\
    \bm{I}_{m/k_{p-1}} \otimes \bm{1}'_{k_{p-1}} \\
    \vdots                                       \\
    \bm{I}_{m/k_{2}} \otimes \bm{1}'_{k_{2}}     \\
  \end{bmatrix}
$$
$\tau$ is time index for most aggregated series,

$k\in \mathcal{K} = \{k_1,\dots,k_p\}$,\quad $k_1=1$,\quad $k_p=m$,\quad $\tau=1,\dots,T/m$.

# Temporal reconciliation: thief package

## Temporal reconciliation: thief package
\fontsize{10}{9.5}\sf

```{r}
#| echo: true
#| message: false
library(thief)
USAccDeaths
thief(USAccDeaths, usemodel = "arima", comb = "struc")
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
#| message: false
# Construct aggregates
aggts <- tsaggregates(USAccDeaths)
aggts[[1]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
aggts[[2]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
#| message: false
aggts[[3]]
```


## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
#| message: false
aggts[[4]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
#| message: false
aggts[[5]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
#| message: false
aggts[[6]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
#| message: false
# Compute forecasts
fc <- list()
for(i in seq_along(aggts)) {
  fc[[i]] <- forecast(auto.arima(aggts[[i]]), h=2*frequency(aggts[[i]]))
}
reconciled <- reconcilethief(fc)
reconciled[[1]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
#| message: false
reconciled[[2]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
#| message: false
reconciled[[3]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
#| message: false
reconciled[[4]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
#| message: false
reconciled[[5]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: true
#| message: false
reconciled[[6]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf

```{r}
#| echo: false
#| message: false
# Plot forecasts before and after reconciliation
par(mfrow=c(2,3))
for(i in seq_along(fc)) {
    plot(reconciled[[i]], main=names(aggts)[i])
    lines(fc[[i]]$mean, col='red')
  }
```

# Temporal reconciliation: Examples

## Temporal reconciliation: M3 monthly series

* Apply temporal reconciliation to all 1428 monthly series from M3 competition
* Forecast horizon $h=18$ months
* ETS and ARIMA models
* Measure percentage difference to base forecasts
* Reconciliation methods:
  * WLS$_H$ (diagonal)
  * WLS$_V$ (diagonal with common variances for same frequency)
  * WLS$_S$ (diagonal/structural)

## Temporal reconciliation: M3 monthly series
\fontsize{9}{9}\sf
\tabcolsep=0.15cm
\centering
\begin{tabular}{lr@{\hskip 0.2cm}rrrrrrrr@{\hskip 0.2cm}rrrrrr}
Aggregation & & & \multicolumn{6}{c}{ETS} & & \multicolumn{5}{c}{ARIMA} \\
\cmidrule{4-9}\cmidrule{11-16}
level & $h$ & & Base & & BU & WLS$_H$ & WLS$_V$ & WLS$_S$ & & Base & & BU & WLS$_H$ & WLS$_V$ & WLS$_S$\\
\midrule
 & & & \multicolumn{13}{c}{RMAE}\\[0.05cm]
Annual           & 1  & & 1.0 & & -19.6 &      -22.0 &      -22.0 & {\bf-25.1}      & & 1.0 & &  -28.6 &      -33.1 &      -32.8 &    {\bf -33.4} \\
Semi-annual      & 3  & & 1.0 & &   0.6 &       -4.0 &       -3.6 & {\bf -5.4}      & & 1.0 & &   -3.4 &       -8.2 &       -8.3 &   {\bf  -9.9} \\
Four-monthly     & 4  & & 1.0 & &   2.0 &       -2.4 &       -2.2 & {\bf -3.0}      & & 1.0 & &   -1.7 &       -5.5 &       -5.9 &   {\bf  -6.7} \\
Quarterly        & 6  & & 1.0 & &   2.4 &       -1.6 &       -1.7 & {\bf -2.8}      & & 1.0 & &   -3.6 &       -7.2 &       -8.1 &   {\bf  -9.1} \\
Bi-monthly       & 9  & & 1.0 & &   0.7 &       -2.9 &       -3.3 & {\bf -4.3}      & & 1.0 & &   -1.5 &       -4.4 &       -5.3 &   {\bf  -6.3} \\
Monthly          & 18 & & 1.0 & &   0.0 &       -2.2 &       -3.2 & {\bf -3.9}      & & 1.0 & &    0.0 &       -0.9 &       -2.9 &   {\bf  -3.4}  \\[0.01cm]
\textit{Average} &    & &   & & \textit{-2.3} & \textit{-5.9} & \textit{-6.0} & {\bf\textit{-7.4}} & &      & & \textit{-6.5} & \textit{-9.9} & \textit{-10.5} & {\bf\textit{ -11.5}} \\[0.1cm]
 & & & \multicolumn{13}{c}{MASE}\\[0.05cm]
Annual           & 1  & &  1.1  & &     -12.1 &      -17.9 &   -17.8 &  {\bf -18.5}  & &       1.3 & &     -25.4 &      -29.9 &      -29.9 &  {\bf -30.2}\\
Semi-annual      & 3  & &  1.0  & &       0.0 &       -6.3 &    -6.0 &  {\bf  -6.9}  & &       1.1 & &      -2.9 &       -8.1 &       -8.2 &  {\bf  -9.4}\\
Four-monthly     & 4  & &  0.9  & &       3.1 &       -3.2 &    -3.0 &  {\bf  -3.4}  & &       0.9 & &      -1.8 &       -6.2 &       -6.5 &  {\bf  -7.1}\\
Quarterly        & 6  & &  0.9  & &       3.2 &       -2.8 &    -2.7 &  {\bf  -3.4}  & &       1.0 & &      -2.6 &       -6.9 &       -7.4 &  {\bf  -8.1}\\
Bi-monthly       & 9  & &  0.9  & &       2.7 &       -2.9 &    -3.0 &  {\bf  -3.7}  & &       0.9 & &      -1.3 &       -5.0 &       -5.5 &  {\bf  -6.3}\\
Monthly          & 18 & &  0.9  & &       0.0 &       -3.7 &    -4.6 &  {\bf  -5.0}  & &       0.9 & &       0.0 &       -1.9 &       -3.2 &  {\bf  -3.7}\\ [0.01cm]
\textit{Average} &    & &       & & \textit{-0.5} & \textit{-6.1} & \textit{-6.2} & {\bf\textit{-6.8}} & &      & & \textit{-5.7} & \textit{-9.7} & \textit{-10.1} & {\bf\textit{ -10.8}}
\end{tabular}

## Example: Accident & emergency services demand

Weekly A\&E demand data: 7 November 2010 to 7 June 2015.\fontsize{11}{11.5}\sf

\begin{tabular}{l}
  \toprule
  Type 1 Departments --- Major A\&E                               \\
  Type 2 Departments --- Single Specialty                         \\
  Type 3 Departments --- Other A\&E/Minor Injury Unit             \\
  Total Attendances                                               \\
  Type 1 Departments --- Major A\&E $>$ 2 hours                   \\
  Type 2 Departments --- Single Specialty $>$ 2 hours             \\
  Type 3 Departments --- Other A\&E/Minor Injury Unit $>$ 2 hours \\
  Total Attendances $>$ 2 hours                                   \\
  Emergency Admissions via Type 1 A\&E                            \\
  Total Emergency Admissions via A\&E                             \\
  Other Emergency Admissions (i.e not via A\&E)                   \\
  Total Emergency Admissions                                      \\
  Number of patients spending $>$ 2 hours from decision to admit to admission
\end{tabular}

## Example: Accident & emergency services demand

\placefig{2.2}{2.2}{height=6.5cm, width=14cm}{AEexample.pdf}

\begin{textblock}{10}(3,1)\fontsize{12}{12}\sf
  \begin{block}{}\centering
    Total emergency admissions via A\&E
  \end{block}
\end{textblock}

## Example: Accident & emergency services demand

Test set: last 52 weeks

\alert{MASE comparison} (ARIMA models)

\begin{tabular}{llllr}
  \toprule
  Aggr. Level & $h$   & Base & Reconciled & Change  \\
  \midrule
  Annual & 1       & 3.4   & 1.9   & $-42.9\%$ \\
  Weekly & 1--52   & 2.0   & 1.9   & $-5.0\%$ \\
  Weekly & 13      & 2.3   & 1.9   & $-16.2\%$ \\
  Weekly & 4       & 1.9   & 1.5   & $-18.6\%$ \\
  Weekly & 1       & 1.6   & 1.3   & $-17.2\%$ \\
\end{tabular}

# Cross-temporal forecast reconciliation

## Cross-temporal forecast reconciliation

\begin{tikzpicture}[baseline=(current  bounding  box.center),
  rel/.append style={shape=ellipse,
    draw=black,
  minimum width=1.5cm,
  minimum height=1cm},
  rel2/.append style={shape=rectangle,
    draw=black,
  minimum width=1.5cm,
  minimum height=1cm},
  connection/.style ={inner sep =0, outer sep =0}]

  \node[rel] at (0, 0) (X){$y_{X,t}$};
  \node[rel] at (2, 0) (Y){$y_{Y,t}$};
  \node[rel] at (1, 1.5) (Tt){$y_{T,t}$};

  \relation{0.2}{X}{Tt};
  \relation{0.2}{Y}{Tt};


  \node[rel2] at (5, 0) (AA){$y_{i,4\tau-3}$};
  \node[rel2] at (7, 0) (AB){$y_{i,4\tau-2}$};
  \node[rel2] at (9, 0) (BA){$y_{i,4\tau-1}$};
  \node[rel2] at (11, 0) (BB){$y_{i,4\tau}$};

  \node[rel2] at (6, 1.5) (A){$x_{i,2\tau-1}^{[2]}$};
  \node[rel2] at (10, 1.5) (B){$x_{i,2\tau}^{[2]}$};
  \node[rel2] at (8, 3) (T){$x_{i,\tau}^{[4]}$};

  \relation{0.2}{AA}{A};
  \relation{0.2}{AB}{A};
  \relation{0.2}{BA}{B};
  \relation{0.2}{BB}{B};

  \relation{0.2}{A}{T};
  \relation{0.2}{B}{T};
\end{tikzpicture}\vspace*{0.7cm}

* $n=3$, $n_a = 1$, $n_b = 2$
* Quarterly series: $m = 2$, $\mathcal{K} = \{1,2,4\}$

## Cross-temporal forecast reconciliation

* $\bm{y}_t=$ series at most temporally disaggregated level, including all cross-sectionally disaggregated and aggregated series.
* $y_{i,t}=$ $i$th element of $\bm{y}_t$, $i=1,\dots,n$.
* For each $i$, we can expand $y_{i,t}$ to include all temporally aggregated variants:
$$\bm{x}_{i,\tau} = \begin{bmatrix}
    {x_{i,\tau}^{[k_p]}} \\
    \vdots               \\
    {\bm{x}_{i,\tau}^{[k_1]}}
  \end{bmatrix}\qquad
\bm{x}_\tau = \begin{bmatrix}
    \bm{x}_{1,\tau} \\
    \vdots          \\
    \bm{x}_{n,\tau}
  \end{bmatrix}.$$

## Cross-temporal forecast reconciliation

\alert{Structural matrix approach}

* $\bm{S}_{cs}=$ structural cross-sectional matrix
* $\bm{S}_{te}=$ structural temporal matrix
* $\bm{S}_{ct} = \bm{S}_{cs} \otimes \bm{S}_{te}$

\vspace*{-0.6cm}

$$\bm{x}_\tau = \bm{S}_{ct} \bm{b}_\tau,\qquad\text{where}\qquad
\bm{b}_\tau = \begin{bmatrix}
    {\bm{x}_{1,\tau}^{[1]}} \\
    \vdots                  \\
    {\bm{x}_{n,\tau}^{[1]}}
  \end{bmatrix}.
$$

## Cross-temporal forecast reconciliation

\full{Smatrix}

\begin{textblock}{5}(0.5,1.5)
\begin{block}{}
\centerline{$\bm{S}_{cs} \otimes \bm{S}_{te} = \bm{S}_{ct}$}
\end{block}
\end{textblock}

## Cross-temporal forecast reconciliation

\alert{Constraint matrix approach}

* $\bm{C}_{cs}=$ cross-sectional constraint matrix
* $\bm{C}_{te}=$ temporal constraint matrix

\vspace*{-0.6cm}

$$\bm{C}_{ct}\bm{x}_\tau = \bm{0}\qquad\text{where}\qquad
\bm{C}_{ct} = \begin{bmatrix}
    (\bm{0}_{(n_a m\times nk^\ast)} ~~ \bm{I}_m \otimes \bm{C}_{cs})\bm{P}' \\
    \bm{I}_n \otimes \bm{C}_{te}
  \end{bmatrix}
$$

* $k^\ast = \displaystyle\sum_{k \in \mathcal{K}\setminus\{k_1\}} \frac{m}{k}$
* $\bm{P}=$ the commutation matrix such that $\bm{P} \text{vec}(\bm{Y}_{\tau}) = \text{vec}(\bm{Y}_{\tau}')$.

# Cross-temporal probabilistic forecast reconciliation

##  Cross-temporal probabilistic forecast reconciliation

\alert{Nonparametric bootstrap}\fontsize{14}{16}\sf

* Simulate future sample paths from all models using bootstrapped residuals, then reconcile them to obtain coherent sample paths.
* Need to generate samples that preserve cross-temporal relationships.
* Draw residual samples of all series at same time from most temporally aggregated level.
* Residuals for other levels obtained using the corresponding time indices.


##  Cross-temporal probabilistic forecast reconciliation
\vspace*{-0.2cm}

```{r}
#| label: bootres
#| output: asis
boot_plot <- function(cols = c("green","blue","red","black")) {
  cat("\\hspace*{-0.8cm}\\begin{tikzpicture}[scale = 0.9, every node/.style={scale=0.9}]\n")
  cat("\\matrix (e1) [matrix of nodes,ampersand replacement=\\&,row sep=0cm,column sep=0cm, nodes= {rectangle, fill=white, inner sep = 1pt, font = {\\fontsize{7}{6}\\selectfont}, minimum width=1em, minimum height=1em,anchor=center}, label={[xshift = 0.5em]above:{\\footnotesize$\\widehat{\\textbf{E}}^{[1]}$}}]\n")
  cat("{\n")
  cat("$T$ \\& ")
  for(j in cols) {
    for(i in seq(4)) {
      cat(paste0("\\pgfuseimage{n",j, "} \\& "))
    }
  }
  cat("\\\\\n")
  cat("$X$ \\& ")
  for(j in cols) {
    for(i in seq(4)) {
      cat(paste0("\\pgfuseimage{n",j, "} \\& "))
    }
  }
  cat("\\\\\n")
  cat("$Y$ \\& ")
  for(j in cols) {
    for(i in seq(4)){
      cat(paste0("\\pgfuseimage{n",j, "} \\& "))
    }
  }
  cat("\\\\\n")
  for(i in seq(16)) {
    cat(paste("\\& ",i))
  }
  cat("\\\\\n")
  cat("};\n")
  cat("\\draw[decorate,thick, decoration={brace, mirror, amplitude=5pt,raise=-1pt}] (e1-4-2.south west) -- (e1-4-17.south east) node[midway, font = {\\fontsize{7}{6}\\selectfont}, yshift = -1em]{Quarterly, $t = 1,\\dots,16$};\n")
  cat("\\matrix (ek) [above= 10mm of e1.north east, anchor=south east, matrix of nodes,ampersand replacement=\\&,row sep=0cm,column sep=0cm, nodes= {rectangle, fill=white, inner sep = 1pt, font = {\\fontsize{7}{6}\\selectfont}, minimum width=1em, minimum height=1em,anchor=center}, label={[xshift = 0.5em]above:{\\footnotesize$\\widehat{\\textbf{E}}^{[2]}$}}]\n")
  cat("{\n")
  cat("$T$ \\& ")
  for(j in cols) {
    for(i in seq(2)){
     cat(paste0("\\pgfuseimage{n",j, "} \\& "))
    }
  }
  cat("\\\\\n")
  cat("$X$ \\& ")
  for(j in cols) {
    for(i in seq(2)){
     cat(paste0("\\pgfuseimage{n",j, "} \\& "))
    }
  }
  cat("\\\\\n")
  cat("$Y$ \\& ")
  for(j in cols) {
    for(i in seq(2)){
     cat(paste0("\\pgfuseimage{n",j, "} \\& "))
    }
  }
  cat("\\\\\n")
  for(i in seq(8)) {
    cat(paste("\\& ",i))
  }
  cat("\\\\\n")
  cat("};\n")
  cat("\\draw[decorate,thick, decoration={brace, mirror, amplitude=5pt,raise=-1pt}] (ek-4-2.south west) -- (ek-4-9.south east) node[midway, font = {\\fontsize{7}{6}\\selectfont}, yshift = -1em]{Semi-annual, $j = 1,\\dots,8$};\n")
  cat("\\matrix (em) [above= 10mm of e1.north west, anchor=south west, matrix of nodes,ampersand replacement=\\&,row sep=0cm,column sep=0cm, nodes= {rectangle, fill=white, inner sep = 1pt, font = {\\fontsize{7}{6}\\selectfont}, minimum width=1em, minimum height=1em,anchor=center}, label={[xshift = 0.5em]above:{\\footnotesize$\\widehat{\\textbf{E}}^{[4]}$}}]\n")
  cat("{\n")
  cat("$T$ \\& ")
  for(j in cols) {
    cat(paste0("\\pgfuseimage{n",j, "}"))
    if(j != cols[4]) cat("\\& ")
  }
  cat("\\\\\n")
  cat("$X$ \\& ")
  for(j in cols) {
    cat(paste0("\\pgfuseimage{n",j, "}"))
    if(j != cols[4]) cat("\\& ")
  }
  cat("\\\\\n")
  cat("$Y$ \\& ")
  for(j in cols) {
    cat(paste0("\\pgfuseimage{n",j, "}"))
    if(j != cols[4]) cat("\\& ")
  }
  cat("\\\\\n")
  for(i in seq(4)) {
    cat(paste("\\& ",i))
  }
  cat("\\\\\n")
  cat("};\n")
  cat("\\draw[decorate,thick, decoration={brace, mirror, amplitude=5pt,raise=-1pt}] (em-4-2.south west) -- (em-4-5.south east) node[midway, font = {\\fontsize{7}{6}\\selectfont}, yshift = -1em]{Annual, $\\tau = 1,\\dots,4$};\n")
  cat("\\end{tikzpicture}\n\n")
}
boot_plot()
```

\begin{textblock}{1.9}(12.9,5.3)
\begin{block}{}\centering
\textcolor[HTML]{7fb97f}{Year 1}\\
\textcolor[HTML]{7fbcff}{Year 2}\\
\textcolor[HTML]{e87f7f}{Year 3}\\
\textcolor[HTML]{7f7f7f}{Year 4}
\end{block}
\end{textblock}

\begin{textblock}{1.9}(12.9,1.6)
\begin{minipage}{1.9cm}
  \begin{block}{}\centering
    \begin{tikzpicture}
      \tikzstyle{every node}=[ellipse,draw,fill=red!15,inner sep=2pt]
      \tikzstyle[level distance=.3cm]
      \tikzstyle[sibling distance=12cm]
      \tikzstyle{level 1}=[sibling distance=10mm,font=\small,set style={{every node}+=[fill=blue!15]}]
      \node{Total}[edge from parent fork down]
      child {node {X}
        }
      child {node {Y}
        };
    \end{tikzpicture}
  \end{block}
\end{minipage}
\end{textblock}

\begin{textblock}{3}(3.5,1.2)\alert{Data}\end{textblock}


##  Cross-temporal probabilistic forecast reconciliation
\vspace*{-0.2cm}

```{r}
#| label: bootres1
#| output: asis
#| dependson: bootres
boot_plot(c("red","black","green","blue"))
```

\begin{textblock}{1.9}(12.9,5.3)
\begin{block}{}\centering
\textcolor[HTML]{7fb97f}{Year 1}\\
\textcolor[HTML]{7fbcff}{Year 2}\\
\textcolor[HTML]{e87f7f}{Year 3}\\
\textcolor[HTML]{7f7f7f}{Year 4}
\end{block}
\end{textblock}

\begin{textblock}{1.9}(12.9,1.6)
\begin{minipage}{1.9cm}
  \begin{block}{}\centering
    \begin{tikzpicture}
      \tikzstyle{every node}=[ellipse,draw,fill=red!15,inner sep=2pt]
      \tikzstyle[level distance=.3cm]
      \tikzstyle[sibling distance=12cm]
      \tikzstyle{level 1}=[sibling distance=10mm,font=\small,set style={{every node}+=[fill=blue!15]}]
      \node{Total}[edge from parent fork down]
      child {node {X}
        }
      child {node {Y}
        };
    \end{tikzpicture}
  \end{block}
\end{minipage}
\end{textblock}

\begin{textblock}{3}(3.5,1.2)\alert{Bootstrap}\end{textblock}

##  Cross-temporal probabilistic forecast reconciliation
\vspace*{-0.2cm}

```{r}
#| label: bootres2
#| output: asis
#| dependson: bootres
boot_plot(c("red","blue","green","blue"))
```

\begin{textblock}{1.9}(12.9,5.3)
\begin{block}{}\centering
\textcolor[HTML]{7fb97f}{Year 1}\\
\textcolor[HTML]{7fbcff}{Year 2}\\
\textcolor[HTML]{e87f7f}{Year 3}\\
\textcolor[HTML]{7f7f7f}{Year 4}
\end{block}
\end{textblock}

\begin{textblock}{1.9}(12.9,1.6)
\begin{minipage}{1.9cm}
  \begin{block}{}\centering
    \begin{tikzpicture}
      \tikzstyle{every node}=[ellipse,draw,fill=red!15,inner sep=2pt]
      \tikzstyle[level distance=.3cm]
      \tikzstyle[sibling distance=12cm]
      \tikzstyle{level 1}=[sibling distance=10mm,font=\small,set style={{every node}+=[fill=blue!15]}]
      \node{Total}[edge from parent fork down]
      child {node {X}
        }
      child {node {Y}
        };
    \end{tikzpicture}
  \end{block}
\end{minipage}
\end{textblock}

\begin{textblock}{3}(3.5,1.2)\alert{Bootstrap}\end{textblock}

\only<2>{\begin{textblock}{8}(3.7,4)
\begin{alertblock}{}
The ``year'' can start in any quarter, giving overlapping blocks.
\end{alertblock}
\end{textblock}}

# Cross-temporal probabilistic reconciliation: Examples

## Quarterly Australian GDP data

\only<1>{\full{IncomeApproach}}
\only<2>{\full{ExpenditureApproach}}
\only<3>{\full{GFCF}}
\only<4>{\full{HFCE}}

## Quarterly Australian GDP data

* Quarterly data: 1984:Q4 -- 2018:Q1

* 95 series

* Time series cross-validation;  initial training set of 10 years.

* One-quarter increase in each training set

* For each training set, compute temporally aggregated series for $k \in \{1,2,4\}$, and produce forecasts up to $h_1=4$, $h_2=2$, and $h_{4}=1$ steps ahead.

* Automatic ARIMA forecasts for all series.

## Quarterly Australian GDP data --- CRPS skill scores
\alert{Reconciliation approaches}\fontsize{13}{14}\sf

* Cross-temporal \textbf{\color{newblue}{bottom-up}} and \textbf{\color{newblue}{partly bottom-up}}

  \begin{tabular}{M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}}
  ct$(shr_{cs}, bu_{te})$ & ct$(wlsv_{te}, bu_{cs})$
  \end{tabular}

* Optimal forecast reconciliation with \textbf{\color{newblue}{overlapping one-step residuals}}

  \begin{tabular}{M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}}
  oct$_o(wlsv)$ & oct$_o(bdshr)$
  \end{tabular}

* Optimal forecast reconciliation with \textbf{\color{newblue}{overlapping and multi-step residuals}}

  \begin{tabular}{M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}}
  oct$_{oh}(hshr)$ & oct$_{oh}(shr)$
  \end{tabular}

## Quarterly Australian GDP data --- CRPS skill scores

\centerline{\textcolor{red}{Worse than benchmark}\qquad \textbf{Best}}\vspace*{-0.3cm}

\centering
\input{tab/AusGDP/sam_crps.tex}

## Quarterly Australian GDP data: Nemenyi test

\placefig{0.5}{1}{width=6.1cm, height = 20cm, trim = 0 300 0 20, clip=true}{figs/AusGDP/ctjb.pdf}
\placefig{8.5}{1.1}{width=6.1cm, height = 20cm, trim = 0 0 0 370, clip=true}{figs/AusGDP/ctjb.pdf}

\only<2>{\begin{textblock}{4}(11.7,2.3)\begin{block}{}
\fontsize{11}{12}\sf
\begin{itemize}\tightlist
\item Mean ranks shown
\item Sig diff if non-overlapping intervals
\end{itemize}
\end{block}\end{textblock}}


## Monthly Australian Tourism Demand

\begin{textblock}{6}(0.2,1.2)
\centering\fontsize{12}{13}\sf
\textbf{Geographical division}\\
\includegraphics[width = 5.8cm]{figs/ausreg2.pdf}\\
\faTimes\\
\textbf{Purpose of travel}\\
{\fontsize{11}{12}\sf Holiday, Visiting friends \& relatives, Business, Other}
\end{textblock}

\begin{textblock}{10}(6.1,1)
\fontsize{11}{14}\sf
\begin{itemize}
\item \textbf{Grouped ts}\newline (geographical divisions $\times$ purpose of travel)

\begin{tabular}{cccccc}
\toprule
  & \textbf{AUS} & \textbf{States} & \textbf{Zones$^\ast$} & \textbf{Regions} & \textbf{Tot}\\
  \midrule
  \textbf{g.d.} & {\color{newblue}1} & {\color{newblue}7} & {\color{newblue}21} & {\color{newblue}76} & 105 \\
  \textbf{p.o.t.} & {\color{newblue}4} & {\color{newblue}28} & {\color{newblue}84} & {\color{avocado}304} & 420\\
  \midrule
  \textbf{Tot} & 5 & 35 & 105 & 380 & \textbf{525}\\
  \bottomrule
\end{tabular}
\centerline{{\color{newblue}$n_a = 221$}, {\color{avocado}$n_b = 304$}, and $\textbf{n = 525}$}

\item \textbf{Temporal framework}, frequencies:\\[0.2cm]
\begin{multicols}{2}
  \begin{itemize}\tightlist
  \item Monthly
  \item Bi-Monthly
  \item Quarterly
  \end{itemize}
  \begin{itemize}\tightlist
  \item Four-Monthly
  \item Semi-Annual
  \item Annual
  \end{itemize}
\end{multicols}
\end{itemize}
\end{textblock}

## Example: Monthly Australian Tourism Demand

* Monthly data: January 1998 to December 2016

* Time series cross-validation; initial training set 10 years.

* One-month increase in each training set

* For each training set, compute temporally aggregated series for $k \in \{1,2,3,4,6,12\}$, and produce forecasts up to $h_2=6$, $h_3=4$, $h_4=3$, $h_6=2$ and $h_{12}=1$ steps ahead.

* Automatic ETS forecasts on log-transformed data

## Example: Australian GDP data --- CRPS skill scores
\alert{Reconciliation approaches}\fontsize{13}{14}\sf

* Cross-temporal \textbf{\color{newblue}{bottom-up}} and \textbf{\color{newblue}{partly bottom-up}}

  \begin{tabular}{M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}}
  ct$(bu)$ & ct$(shr_{cs}, bu_{te})$ & ct$(wlsv_{te}, bu_{cs})$
  \end{tabular}

* Optimal forecast reconciliation with \textbf{\color{newblue}{one-step residuals}}

    \begin{tabular}{M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}}
    oct$(ols)$ & oct$(struc)$ & oct$(wlsv)$ & oct$(bdshr)$
    \end{tabular}

* Optimal forecast reconciliation with \textbf{\color{newblue}{multi-step residuals}}

    \begin{tabular}{M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}}
    oct$_h(hbshr)$ & oct$_h(bshr)$ & oct$_h(hshr)$ & oct$_h(shr)$
    \end{tabular}

## Example: Australian tourism data -- CRPS skill scores
\fontsize{12}{13}\sf\vspace*{0.2cm}

\centerline{\textcolor{red}{Worse than benchmark}\qquad \textbf{Best}}

\centering
\footnotesize
\begin{tabular}[t]{lrr}
& \textbf{$\forall k \in \{12,6,4,3,2,1\}$} & \textbf{$k = 1$}\\
\midrule
base                      & \cellcolor{LightOrange!30} {1.000}  & \cellcolor{LightOrange!30} {1.000} \\
ct$(bu)$                  & \textcolor{red}{1.321}              & \textcolor{red}{1.077} \\
ct$(shr_{cs}, bu_{te})$   & \textcolor{red}{1.057}              & {0.976} \\
ct$(wlsv_{te}, bu_{cs})$  & \textcolor{red}{1.062}              & {0.976}\\
oct$(ols)$                & {0.989}                             & {0.982}\\
oct$(struc)$              & {0.982}                             & {0.970}\\
oct$(wlsv)$               & {0.987}                             & {0.952} \\
oct$(bdshr)$              & {0.975}                             & {\textbf{0.949}} \\
oct$_h(hbshr)$            & {0.989}                             & {0.982} \\
oct$_h(bshr)$             & {0.994}                             & {0.988}\\
oct$_h(hshr)$             & {\textbf{0.969}}                    & {0.953}\\
oct$_h(shr)$              & \textcolor{red}{1.007}              & \textcolor{red}{1.000}
\end{tabular}

## MCB Nemenyi test

\placefig{0}{1.2}{width=16cm, height=200cm, trim = 0 520 0 30, clip=TRUE}{figs/VN525/ctjb_more.pdf}

\begin{textblock}{15}(0.2,7)
\begin{itemize}\tightlist
\item mean ranks shown
\item significant differences if non-overlapping intervals
\end{itemize}
\end{textblock}

# Software

## Software
\fontsize{11}{12}\sf\vspace*{0.3cm}

\hspace*{-0.6cm}\begin{tabular}{llP{1.7cm}cP{1.7cm}c}
\toprule
Package                                                                      & Language  & Cross-sectional  & Temporal    & Cross-temporal  & Probabilistic\\
\midrule
\texttt{\href{https://pkg.earo.me/hts/}{hts}}
    & R         & \checkmark       &             &                 & \\
\texttt{\href{http://pkg.robjhyndman.com/thief/}{thief}}
    & R         &                  & \checkmark  &                 & \\
\texttt{\href{https://fable.tidyverts.org}{fable}}
    & R         & \checkmark       &             &                 & \checkmark\\
\texttt{\href{https://danigiro.github.io/FoReco/}{FoReco}}
    & R         & \checkmark       & \checkmark  & \checkmark      & \checkmark\\
\texttt{\href{https://angelpone.github.io/pyhts/}{pyhts}}
    & Python    & \checkmark       & \checkmark  &                 & \\
\texttt{\href{https://nixtla.github.io/hierarchicalforecast/}{hierarchicalforecast}}
    & Python    & \checkmark       &             &                 & \checkmark \\
\bottomrule
\end{tabular}

* `hts`, `thief`, and `FoReco` use `ts` objects
* `fable` uses `tsibble` objects
* `fable` has plans to implement temporal and cross-temporal reconciliation

## Thanks!

\placefig{0}{1.2}{trim = 10 45 0 0, clip=TRUE, width=10cm, height=2.5cm}{roman}
\placefig{2}{1.2}{trim = 0 40 0 0, clip=TRUE, width=10cm, height=2.5cm}{george}
\placefig{4}{1.2}{trim = 0 10 0 0, clip=TRUE, width=10cm, height=2.5cm}{hanlin}
\placefig{6}{1.2}{trim = 10 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{earowang}
\placefig{8}{1.2}{trim = 0 15 0 0, clip=TRUE, width=10cm, height=2.5cm}{alanlee}
\placefig{10}{1.2}{trim = 30 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{mitch}
\placefig{12}{1.2}{trim = 15 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{shanika}
\placefig{14}{1.2}{trim = 40 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{tas}

\placefig{0}{3.8}{trim = 30 10 30 0, clip=TRUE, width=10cm, height=2.5cm}{puwasala}
\placefig{2}{3.8}{trim = 0 10 0 0, clip=TRUE, width=10cm, height=2.5cm}{fotios}
\placefig{4}{3.8}{trim = 100 30 50 20, clip=TRUE, width=10cm, height=2.5cm}{nikos}
\placefig{6}{3.8}{trim = 50 30 0 0, clip=TRUE, width=10cm, height=2.5cm}{souhaib}
\placefig{8}{3.8}{trim = 110 40 50 0, clip=TRUE, width=10cm, height=2.5cm}{james}
\placefig{10}{3.8}{trim = 40 40 0 0, clip=TRUE, width=10cm, height=2.5cm}{mahdi}
\placefig{12}{3.8}{trim = 50 50 0 0, clip=TRUE, width=10cm, height=2.5cm}{christoph}
\placefig{14}{3.8}{trim = 50 50 0 20, clip=TRUE, width=10cm, height=2.5cm}{fin}

\placefig{0}{6.4}{trim = 10 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{berwin}
\placefig{2}{6.4}{trim = 10 20 0 0, clip=TRUE, width=10cm, height=2.5cm}{galit}
\placefig{4}{6.4}{trim = 10 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{mahsa}
\placefig{6}{6.4}{trim = 30 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{evan}
\placefig{8}{6.4}{trim = 5 25 0 0, clip=TRUE, width=10cm, height=2.5cm}{bahman}
\placefig{10}{6.4}{trim = 0 40 0 0, clip=TRUE, width=10cm, height=2.5cm}{pablo}
\placefig{12}{6.4}{trim = 0 40 0 0, clip=TRUE, width=10cm, height=2.5cm}{danielegiro}
\placefig{14}{6.4}{trim = 0 0 0 30, clip=TRUE, width=10cm, height=2.5cm}{tommy}

## More information
\fontsize{18}{20}\sf

\href{https://robjhyndman.com/fr2023}{\includegraphics[width=0.5cm]{figs/slide}\, robjhyndman.com/fr2023}

\href{https://robjhyndman.com}{\faicon{home} robjhyndman.com}

\href{https://twitter.com/robjhyndman}{\faicon{twitter} @robjhyndman}

\href{https://aus.social/@robjhyndman}{\includegraphics[width=0.5cm]{figs/mastodon}\, aus.social/@robjhyndman}

\href{https://github.com/robjhyndman}{\faicon{github}  @robjhyndman}

\href{mailto:rob.hyndman@monash.edu}{\faicon{envelope}  rob.hyndman@monash.edu}

\begin{textblock}{6.2}(0,8.8)\pgfsetfillopacity{0.65}
\begin{beamercolorbox}[wd=4.7cm]{block body}
\fontsize{6}{6}\sf\color[RGB]{72,45,34}\href{https://www.flaticon.com/free-icons/presentation}{Presentation icon created by orvipixel - Flaticon}
  \end{beamercolorbox}
\end{textblock}


\nocite{Di_FonGir2022a,temporal-hierarchies,ctprob}
