---
title: Forecast reconciliation
subtitle: 4. Temporal & cross-temporal forecast reconcilation
author: Rob J Hyndman
pdf-engine: pdflatex
fig-width: 9
fig-height: 4.5
format:
  beamer:
    theme: monash
    aspectratio: 169
    fontsize: 14pt
    section-titles: false
    knitr:
      opts_chunk:
        dev: "CairoPDF"
include-in-header: header.tex
cite-method: biblatex
bibliography: hts.bib
biblio-title: References
keep-tex: true
execute:
  echo: false
  message: false
  warning: false
  cache: true
---

```{r}
source("setup.R")
```

## Outline

\vspace*{0.4cm}\tableofcontents

## Notation reminder

\begin{textblock}{8.5}(0.2,1.5)
Every collection of time series with linear constraints can be written as
\centerline{\colorbox[RGB]{210,210,210}{$\bY_{t}=\color{blue}\bS\color{red}\bm{b}_{t}$}}
\vspace*{-0.9cm}\begin{itemize}\parskip=0cm\itemsep=0cm
\item $\by_t=$ vector of all series at time $t$
\item $ y_{\text{Total},t}= $ aggregate of all series at time
$t$.
\item $ y_{X,t}= $ value of series $X$ at time $t$.
\item $\color{red}{\bm{b}_t}=$ vector of most disaggregated series at time $t$
\item $\color{blue}{\bS}=$ ``summing matrix'' containing the linear constraints.
\end{itemize}
\end{textblock}

\begin{textblock}{5.7}(11.4,0.1)
\begin{minipage}{4cm}
\begin{block}{}\centering
\begin{tikzpicture}
\tikzstyle{every node}=[ellipse,draw,fill=red!15,inner sep=2pt]
\tikzstyle[level distance=.3cm]
\tikzstyle[sibling distance=12cm]
\tikzstyle{level 1}=[sibling distance=10mm,font=\small,set style={{every node}+=[fill=blue!15]}]
\node{Total}[edge from parent fork down]
 child {node {A}
 }
 child {node {B}
 }
 child {node {C}
 };
\end{tikzpicture}
\end{block}
\end{minipage}
\end{textblock}

\only<1>{\begin{textblock}{5.7}(9.4,2.8)\fontsize{14}{15}\sf
\begin{align*}
\bY_{t}&= \begin{pmatrix}
  y_{\text{Total},t}\\
  y_{A,t}\\
  y_{B,t}\\
  y_{C,t}
  \end{pmatrix}  \\
  &= {\color{blue}\underbrace{\begin{pmatrix}
                1 & 1 & 1 \\
                1 & 0 & 0 \\
                0 & 1 & 0\\
                0 & 0 & 1
                \end{pmatrix}}_{\bS}}
     {\color{red}\underbrace{\begin{pmatrix}
       y_{A,t}\\y_{B,t}\\y_{C,t}
       \end{pmatrix}}_{\bm{b}_{t}}}
\end{align*}
\end{textblock}}
\only<2>{\begin{textblock}{5.7}(9.4,3.2)\fontsize{14}{15}\sf
\begin{alertblock}{}
\begin{itemize}\itemsep=0.1cm
\item Base forecasts: $\hat{\bm{y}}_{T+h|T}$
\item Reconciled forecasts: $\tilde{\bm{y}}_{T+h|T}=\bS\bm{G}\hat{\bm{y}}_{T+h|T}$
\item MinT: $\bG = (\bS'\bm{W}_h^{-1}\bS)^{-1}\bS'\bm{W}_h^{-1}$ where $\bm{W}_h$ is covariance matrix of base forecast errors.
\end{itemize}
\end{alertblock}
\end{textblock}}

# Temporal reconciliation

## Temporal reconciliation

\begin{textblock}{7}(1,1.9)
\begin{tikzpicture}
\tikzstyle{every node}=[ellipse,draw,inner sep=0.2pt,fill=red!15,font=\small]
\tikzstyle[level distance=.1cm]
\tikzstyle[sibling distance=3cm]
\tikzstyle{level 1}=[sibling distance=18mm,set style={{every node}+=[fill=yellow]}]
\node{Annual}[edge from parent fork down]
   child {node {Q$_1$}}
   child {node {Q$_2$}}
   child {node {Q$_3$}}
   child {node {Q$_4$}};
\end{tikzpicture}
\end{textblock}

\begin{textblock}{8.5}(8.3,1.9)
$$\bm{y}_j =
  \begin{bmatrix}
    y_j \\
    y_{j,1}^{[1]}\\
    y_{j,2}^{[1]}\\
    y_{j,3}^{[1]}\\
    y_{j,4}^{[1]}
  \end{bmatrix}
  \qquad
  \bm{S} = \begin{bmatrix}
    1 & 1 & 1 & 1 \\
    1 & 0 & 0 & 0 \\
    0 & 1 & 0 & 0  \\
    0 & 0 & 1 & 0  \\
    0 & 0 & 0 & 1
  \end{bmatrix}
$$
\end{textblock}

## Temporal reconciliation

\begin{textblock}{7}(0.1,1.9)
\begin{tikzpicture}
\tikzstyle{every node}=[ellipse,draw,inner sep=0.2pt,fill=red!15,font=\small]
\tikzstyle[level distance=.1cm]
\tikzstyle[sibling distance=3cm]
\tikzstyle{level 1}=[sibling distance=42mm,set style={{every node}+=[fill=blue!15]}]
\tikzstyle{level 2}=[sibling distance=18mm,set style={{every node}+=[fill=yellow]}]
\node{Annual}[edge from parent fork down]
 child {node {Semi-Annual$_1$}
   child {node {Q$_1$}}
   child {node {Q$_2$}}
  }
 child {node {Semi-Annual$_2$}
   child {node {Q$_3$}}
   child {node {Q$_4$}}
  };
\end{tikzpicture}
\end{textblock}

\begin{textblock}{8.5}(8.3,1.9)
$$\bm{y}_j =
  \begin{bmatrix}
    y_j \\
    y_{j,1}^{[2]}\\
    y_{j,2}^{[2]}\\
    y_{j,1}^{[1]}\\
    y_{j,2}^{[1]}\\
    y_{j,3}^{[1]}\\
    y_{j,4}^{[1]}
  \end{bmatrix}
  \qquad
  \bm{S} = \begin{bmatrix}
    1 & 1 & 1 & 1 \\
    1 & 1 & 0 & 0 \\
    0 & 0 & 1 & 1 \\
    1 & 0 & 0 & 0 \\
    0 & 1 & 0 & 0  \\
    0 & 0 & 1 & 0  \\
    0 & 0 & 0 & 1
  \end{bmatrix}
$$
\end{textblock}

## Temporal reconciliation

\only<1>{\begin{tikzpicture}
\tikzstyle{every node}=[ellipse,draw,inner sep=0.2pt,fill=red!15,font=\small]
\tikzstyle[level distance=.1cm]
\tikzstyle[sibling distance=7cm]
\tikzstyle{level 1}=[sibling distance=72mm,set style={{every node}+=[fill=blue!15]}]
\tikzstyle{level 2}=[sibling distance=36mm,set style={{every node}+=[fill=yellow]}]
\tikzstyle{level 3}=[sibling distance=12mm,font=\scriptsize,set style={{every node}+=[fill=green]}]
\node{Annual}[edge from parent fork down]
 child {node {Semi-Annual$_1$}
   child {node {Q$_1$}
     child {node {\scriptsize M$_1$}}
     child {node {\scriptsize M$_2$}}
     child {node {\scriptsize M$_3$}}
   }
   child {node {Q$_2$}
     child {node {\scriptsize M$_4$}}
     child {node {\scriptsize M$_5$}}
     child {node {\scriptsize M$_6$}}
   }
 }
 child {node {Semi-Annual$_2$}
   child {node {Q$_3$}
     child {node {\scriptsize M$_7$}}
     child {node {\scriptsize M$_8$}}
     child {node {\scriptsize M$_9$}}
   }
   child {node {Q$_4$}
     child {node {\scriptsize M$_{10}$}}
     child {node {\scriptsize M$_{11}$}}
     child {node {\scriptsize M$_{12}$}}
   }
 };
\end{tikzpicture}}
\only<2->{\begin{tikzpicture}
\tikzstyle{every node}=[ellipse,draw,inner sep=0.2pt,fill=red!15,font=\small]
\tikzstyle[level distance=.1cm]
\tikzstyle[sibling distance=7cm]
\tikzstyle{level 1}=[sibling distance=48mm,set style={{every node}+=[fill=blue!15]}]
\tikzstyle{level 2}=[sibling distance=24mm,set style={{every node}+=[fill=yellow]}]
\tikzstyle{level 3}=[sibling distance=12mm,set style={{every node}+=[fill=green]}]
\node{Annual}[edge from parent fork down]
 child {node {FourM$_1$}
   child {node {BiM$_1$}
     child {node {\scriptsize M$_1$}}
     child {node {\scriptsize M$_2$}}
   }
   child {node {BiM$_2$}
     child {node {\scriptsize M$_3$}}
     child {node {\scriptsize M$_4$}}
   }
 }
 child {node {FourM$_2$}
   child {node {BiM$_3$}
     child {node {\scriptsize M$_5$}}
     child {node {\scriptsize M$_6$}}
   }
   child {node {BiM$_4$}
     child {node {\scriptsize M$_7$}}
     child {node {\scriptsize M$_8$}}
   }
 }
  child {node {FourM$_3$}
   child {node {BiM$_5$}
     child {node {\scriptsize M$_9$}}
     child {node {\scriptsize M$_{10}$}}
   }
   child {node {BiM$_6$}
     child {node {\scriptsize M$_{11}$}}
     child {node {\scriptsize M$_{12}$}}
   }
 };
\end{tikzpicture}}\pause

\vspace*{10cm}

\only<3>{\begin{textblock}{14}(1,6.7)
\begin{alertblock}{}
\begin{itemize}
\item[\color{white}\ding{229}] Forecast series at each available frequency.
\item[\color{white}\ding{229}] Optimally combine forecasts within the same year.
\end{itemize}
\end{alertblock}
\end{textblock}}

## Temporal reconciliation
\fontsize{11}{11}\sf

$$
\bm{y}_i=\begin{bmatrix}
  y_{i}^{[12]} \\
  \bm{y}_{i}^{[6]} \\
  \bm{y}_{i}^{[4]} \\
  \bm{y}_{i}^{[3]} \\
  \bm{y}_i^{[2]} \\
  \bm{y}_i^{[1]}
  \end{bmatrix}
  \qquad
  \bm{S} = \begin{bmatrix}
                1 & 1 & 1 & 1 & 1~~~1~~~1~~~1 & 1 & 1& 1& 1\\
                1 & 1 & 1 & 1 & 1~~~1~~~0~~~0 & 0 & 0& 0& 0\\
                0 & 0 & 0 & 0 & 0~~~0~~~1~~~1 & 1 & 1& 1& 1\\
                1 & 1 & 1 & 1 & 0~~~0~~~0~~~0 & 0 & 0& 0& 0\\
                0 & 0 & 0 & 0 & 1~~~1~~~1~~~1 & 0 & 0& 0& 0\\
                0 & 0 & 0 & 0 & 0~~~0~~~0~~~0 & 1 & 1& 1& 1\\
                1 & 1 & 1 & 0 & 0~~~0~~~0~~~0 & 0 & 0& 0& 0\\
                  &   &   &   & \vdots        &   &  &  &  \\
                0 & 0 & 0 & 0 & 0~~~0~~~0~~~0 & 0 & 1& 1& 1\\
                1 & 1 & 0 & 0 & 0~~~0~~~0~~~0 & 0 & 0& 0& 0\\
                  &   &   &   & \vdots        &   &  &  &  \\
                0 & 0 & 0 & 0 & 0~~~0~~~0~~~0 & 0 & 0& 1& 1\\[0.2cm]
                \phantom{\vdots}  &   &   &  & \bm{I}_{12} &  &  &  &
  \end{bmatrix}
$$

## Temporal reconciliation
\fontsize{14}{15}\sf

For a time series  $y_1,\dots,y_T$, observed at frequency $m$, we generate aggregate series
\begin{alertblock}{}\vspace*{-0.1cm}
\[
y_j^{\left[k\right]} = \sum^{jk}_{t=1+(j-1)k}{y_t},\qquad \text{for $j = 1,\dots,\lfloor T/k\rfloor$}
\]
\end{alertblock}
* $k \in F(m)=\{\text{factors of $m$}\}$.
* A single unique hierarchy is only possible when there are no coprime pairs in $F(m)$.
* $M_k=m/k$ is seasonal period of aggregated series.
* Proposed by Athanasopoulos, Hyndman, Kourentzes, Petropoulos (*EJOR*, 2017)

# Temporal reconciliation: thief package

## Temporal reconciliation: thief package
\fontsize{10}{10}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
library(thief)
USAccDeaths
thief(USAccDeaths, usemodel = "arima", comb = "struc")
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
# Construct aggregates
aggts <- tsaggregates(USAccDeaths)
aggts[[1]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
aggts[[2]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
aggts[[3]]
```


## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
aggts[[4]]
```


## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
aggts[[5]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
aggts[[6]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
# Compute forecasts
fc <- list()
for(i in seq_along(aggts))
  fc[[i]] <- forecast(auto.arima(aggts[[i]]), h=2*frequency(aggts[[i]]))
# Reconcile forecasts
reconciled <- reconcilethief(fc)
reconciled[[1]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
reconciled[[2]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
reconciled[[3]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
reconciled[[4]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
reconciled[[5]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: true
#| message: false
reconciled[[6]]
```

## Temporal reconciliation: thief package
\fontsize{10}{11}\sf\vspace*{0.2cm}

```{r}
#| echo: false
#| message: false
# Plot forecasts before and after reconcilation
par(mfrow=c(2,3))
for(i in seq_along(fc)) {
  plot(reconciled[[i]], main=names(aggts)[i])
  lines(fc[[i]]$mean, col='red')
}
```

# Temporal reconciliation: Examples

## Temporal reconciliation: M3 monthly series

* Apply temporal reconciliation to all 1428 monthly series from M3 competition
* Forecast horizon $h=18$ months
* ETS and ARIMA models
* Measure percentage difference to base forecasts
* Reconciliation methods:
  * WLS$_H$ (diagonal)
  * WLS$_V$ (diagonal with common variances for same frequency)
  * WLS$_S$ (diagonal/structural)

## Temporal reconciliation: M3 monthly series
\fontsize{9}{9}\sf\vspace*{-0.2cm}

\hspace*{-0.8cm}
\begin{tabular}{lr@{\hskip 0.2cm}rrrrrrrr@{\hskip 0.2cm}rrrrrr}
\toprule
\multicolumn{16}{c}{}\\[-0.4cm]
Aggregation & & & \multicolumn{6}{c}{ETS} & & \multicolumn{5}{c}{ARIMA} \\
\cmidrule{4-9}\cmidrule{11-16}
\multicolumn{16}{c}{}\\[-0.4cm]
level & $h$ & & Base & & BU & WLS$_H$ & WLS$_V$ & WLS$_S$ & & Base & & BU & WLS$_H$ & WLS$_V$ & WLS$_S$\\
\cmidrule{1-2}\cmidrule{4-4}\cmidrule{6-9}\cmidrule{11-11} \cmidrule{13-16}
\multicolumn{16}{c}{}\\[-0.3cm]
 & & & \multicolumn{13}{c}{RMAE}\\[0.05cm]
Annual           & 1  & & 1.0 & & -19.6 &      -22.0 &      -22.0 & {\bf-25.1}      & & 1.0 & &  -28.6 &      -33.1 &      -32.8 &    {\bf -33.4} \\
Semi-annual      & 3  & & 1.0 & &   0.6 &       -4.0 &       -3.6 & {\bf -5.4}      & & 1.0 & &   -3.4 &       -8.2 &       -8.3 &   {\bf  -9.9} \\
Four-monthly     & 4  & & 1.0 & &   2.0 &       -2.4 &       -2.2 & {\bf -3.0}      & & 1.0 & &   -1.7 &       -5.5 &       -5.9 &   {\bf  -6.7} \\
Quarterly        & 6  & & 1.0 & &   2.4 &       -1.6 &       -1.7 & {\bf -2.8}      & & 1.0 & &   -3.6 &       -7.2 &       -8.1 &   {\bf  -9.1} \\
Bi-monthly       & 9  & & 1.0 & &   0.7 &       -2.9 &       -3.3 & {\bf -4.3}      & & 1.0 & &   -1.5 &       -4.4 &       -5.3 &   {\bf  -6.3} \\
Monthly          & 18 & & 1.0 & &   0.0 &       -2.2 &       -3.2 & {\bf -3.9}      & & 1.0 & &    0.0 &       -0.9 &       -2.9 &   {\bf  -3.4}  \\[0.01cm]
\textit{Average} &    & &   & & \textit{-2.3} & \textit{-5.9} & \textit{-6.0} & {\bf\textit{-7.4}} & &      & & \textit{-6.5} & \textit{-9.9} & \textit{-10.5} & {\bf\textit{ -11.5}} \\[0.1cm]
 & & & \multicolumn{13}{c}{MASE}\\[0.05cm]
Annual           & 1  & &  1.1  & &     -12.1 &      -17.9 &   -17.8 &  {\bf -18.5}  & &       1.3 & &     -25.4 &      -29.9 &      -29.9 &  {\bf -30.2}\\
Semi-annual      & 3  & &  1.0  & &       0.0 &       -6.3 &    -6.0 &  {\bf  -6.9}  & &       1.1 & &      -2.9 &       -8.1 &       -8.2 &  {\bf  -9.4}\\
Four-monthly     & 4  & &  0.9  & &       3.1 &       -3.2 &    -3.0 &  {\bf  -3.4}  & &       0.9 & &      -1.8 &       -6.2 &       -6.5 &  {\bf  -7.1}\\
Quarterly        & 6  & &  0.9  & &       3.2 &       -2.8 &    -2.7 &  {\bf  -3.4}  & &       1.0 & &      -2.6 &       -6.9 &       -7.4 &  {\bf  -8.1}\\
Bi-monthly       & 9  & &  0.9  & &       2.7 &       -2.9 &    -3.0 &  {\bf  -3.7}  & &       0.9 & &      -1.3 &       -5.0 &       -5.5 &  {\bf  -6.3}\\
Monthly          & 18 & &  0.9  & &       0.0 &       -3.7 &    -4.6 &  {\bf  -5.0}  & &       0.9 & &       0.0 &       -1.9 &       -3.2 &  {\bf  -3.7}\\ [0.01cm]
\textit{Average} &    & &       & & \textit{-0.5} & \textit{-6.1} & \textit{-6.2} & {\bf\textit{-6.8}} & &      & & \textit{-5.7} & \textit{-9.7} & \textit{-10.1} & {\bf\textit{ -10.8}} \\[0.1cm]
\bottomrule
\end{tabular}

## Example: Accident & emergency services demand

Weekly A\&E demand data: 7 November 2010 to 7 June 2015.\fontsize{11}{11.5}\sf

\begin{tabular}{l}
\toprule
Type 1 Departments --- Major A\&E	\\
Type 2 Departments --- Single Specialty	\\
Type 3 Departments --- Other A\&E/Minor Injury Unit \\
Total Attendances \\
Type 1 Departments --- Major A\&E $>$ 4 hours \\
Type 2 Departments --- Single Specialty $>$ 4 hours \\
Type 3 Departments --- Other A\&E/Minor Injury Unit $>$ 4 hours \\
Total Attendances $>$ 4 hours \\
Emergency Admissions via Type 1 A\&E \\
Total Emergency Admissions via A\&E \\
Other Emergency Admissions (i.e not via A\&E) \\
Total Emergency Admissions \\
Number of patients spending $>$ 4 hours from decision to admit to admission
\end{tabular}

## Example: Accident & emergency services demand

\placefig{2.2}{2.2}{height=6.5cm, width=14cm}{AEexample.pdf}

\begin{textblock}{10}(3,1)\fontsize{12}{12}\sf
\begin{block}{}\centering
Total emergency admissions via A\&E
\end{block}
\end{textblock}

## Example: Accident & emergency services demand

Test set: last 52 weeks

\alert{MASE comparison} (ARIMA models)

\begin{tabular}{llllr}
\toprule
Aggr. Level 		& $h$   & Base  & Reconciled & Change \\
\midrule
Annual & 1     	& 3.4   & 1.9   & $-42.9\%$ \\
Weekly & 1--52 	& 2.0   & 1.9   & $-5.0\%$ \\
Weekly & 13    	& 2.3   & 1.9   & $-16.2\%$ \\
Weekly & 4     	& 1.9   & 1.5   & $-18.6\%$ \\
Weekly & 1     	& 1.6   & 1.3   & $-17.2\%$
\end{tabular}

# Cross-temporal reconciliation

## Cross-temporal reconciliation

\begin{block}{}
\begin{itemize}
\item Kourentzes, Athanasopoulos (\emph{ATR}, 2019)
\item Punia, Singh, Madaan (\emph{C\&IE}, 2020)
\item Di Fonzo,  Girolimetto (2020)
\end{itemize}
\end{block}\pause

\begin{alertblock}{ISF talks coming up!}
\begin{itemize}
\item[\ding{229}] Mitch O'Hara-Wild: \emph{Probabilistic cross-temporal hierarchies in fable} (in about 3 hours)
\item[\ding{229}] Tommi Di Fonzo: \emph{Non-negative cross-temporal forecast reconciliation. An application to the Australian domestic tourism flows} (in about 11 hours).
\end{itemize}
\end{alertblock}

\vspace*{10cm}


## Daniele and Tommy's papers

\nocite{Di_FonGir2022a,temporal-hierarchies}


# Cross-temporal probabilistic forecast reconciliation

##  Cross-temporal probabilistic forecast reconciliation

## Thanks!

\placefig{0}{1.4}{trim = 10 45 0 0, clip=TRUE, width=10cm, height=2.5cm}{roman}
\placefig{2}{1.4}{trim = 20 20 0 0, clip=TRUE, width=10cm, height=2.7cm}{george}
\placefig{4}{1.4}{trim = 0 10 0 0, clip=TRUE, width=10cm, height=2.5cm}{hanlin}
\placefig{6}{1.4}{trim = 10 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{earowang}
\placefig{8}{1.4}{trim = 0 15 0 0, clip=TRUE, width=10cm, height=2.5cm}{alanlee}
\placefig{10}{1.4}{trim = 30 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{mitch}
\placefig{12}{1.4}{trim = 15 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{shanika}
\placefig{14}{1.4}{trim = 40 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{tas}

\placefig{0}{3.9}{trim = 30 10 30 0, clip=TRUE, width=10cm, height=2.5cm}{puwasala}
\placefig{2}{3.9}{trim = 0 10 0 0, clip=TRUE, width=10cm, height=2.5cm}{fotios}
\placefig{4}{3.9}{trim = 100 30 50 20, clip=TRUE, width=10cm, height=2.5cm}{nikos}
\placefig{6}{3.9}{trim = 50 30 0 0, clip=TRUE, width=10cm, height=2.5cm}{souhaib}
\placefig{8}{3.9}{trim = 110 40 50 0, clip=TRUE, width=10cm, height=2.5cm}{james}
\placefig{10}{3.9}{trim = 40 40 0 0, clip=TRUE, width=10cm, height=2.5cm}{mahdi}
\placefig{12}{3.9}{trim = 50 50 0 0, clip=TRUE, width=10cm, height=2.5cm}{christoph}
\placefig{14}{3.9}{trim = 50 50 0 20, clip=TRUE, width=10cm, height=2.5cm}{fin}

\placefig{0}{6.4}{trim = 10 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{berwin}
\placefig{2}{6.4}{trim = 10 20 0 0, clip=TRUE, width=10cm, height=2.5cm}{galit}
\placefig{4}{6.4}{trim = 10 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{mahsa}
\placefig{6}{6.4}{trim = 10 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{florian}
\placefig{8}{6.4}{trim = 30 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{evan}
\placefig{10}{6.4}{trim = 5 5 0 0, clip=TRUE, width=10cm, height=2.5cm}{vassilis}
\placefig{12}{6.4}{trim = 90 0 0 0, clip=TRUE, width=10cm, height=2.5cm}{carla}
\placefig{14}{6.4}{trim = 0 40 0 0, clip=TRUE, width=10cm, height=2.5cm}{pablo}

## More information
\fontsize{18}{20}\sf

\href{https://robjhyndman.com/fr2023}{\includegraphics[width=0.5cm]{figs/slide}\, robjhyndman.com/fr2023}

\href{https://robjhyndman.com}{\faicon{home} robjhyndman.com}

\href{https://twitter.com/robjhyndman}{\faicon{twitter} @robjhyndman}

\href{https://aus.social/@robjhyndman}{\includegraphics[width=0.5cm]{figs/mastodon}\, aus.social/@robjhyndman}

\href{https://github.com/robjhyndman}{\faicon{github}  @robjhyndman}

\href{mailto:rob.hyndman@monash.edu}{\faicon{envelope}  rob.hyndman@monash.edu}

\begin{textblock}{6.2}(0,8.8)\pgfsetfillopacity{0.65}
\begin{beamercolorbox}[wd=4.7cm]{block body}
\fontsize{6}{6}\sf\color[RGB]{72,45,34}\href{https://www.flaticon.com/free-icons/presentation}{Presentation icon created by orvipixel - Flaticon}
\end{beamercolorbox}
\end{textblock}
